The Feasibility of Stylometry as a Service

### 2013-12-11 paper/paper.tex
Added reference, filling in section.

@@

>>>>

We do not place an specific performance metrics on the service other
than that it should be reasonably responsive.  Since JStylo relies on
Weka \cite{Hall:2009:WDM:1656274.1656278} to implement the machine
learning algorithms, this server should have a decent amount of RAM.

@@

The security features need for a stylometric service are
authentication, confidentiality, integrity, and repudiation.

{\bf Authentication.}  Users must be able to authenticate the
service.  We propose that if the service is using HTTPS with a server
certificate signed by a trusted certificate authority that this will
suffice.  However, when running behind a Tor Hidden Service, this is
slightly more complicated.  The service can sign the onion address
that it provides and Tor will ensure that the address maps to the
service.  The signature would correspond to a trusted certificate
authority issued certificate.  Mutual authentication, or
authentication of the users should \emph{not} be conducted as this
would either compromise the user's identity.

{\bf Confidentiality.} The service must protect the confidentiality of
the user's data.  The user is trusting the service with their corpus
and document to anonymize and that must be revealed to unauthroized
users.  However, one of the goals of this service is to allow multiple
authors to collaborate.  In this case, the confidentiality
requirements are more interesting.  We don't specifiy an
implementation, but there are various techniques that could satisfy
this requirement.

Besides multi-authors, the service is also multi-user.
